Speeding up prediction performance of the BDT-based models

### 2017-11-10 acat_paper/paper.tex
polish1

However, the difference in working time is not so significant - 2.5 times and 50 times, respectively. This is due to the principles of the CPU caching and the size of our dataset. Since the Decision Tensor takes up a very large amount of memory and does not fit into the CPU cache because, almost every lookup results in reading from the RAM. CatBoost models are small enough to fit into the cache. Since our benchmark consists only of model applications, CatBoost models are not moved out of the cache. In real applications, the CatBoost model will most likely not sit in the cache alone and will be even slower because of this. On the contrary the performance of Decision Tensor Ensemble will not degrade due to that fact.

>>>>

However, the difference in working time is not so significant - 2.5 times and 50 times, respectively. This is due to the principles of the CPU caching and the size of our dataset. Since the Decision Tensor occupies significant amount of memory and does not fit into the CPU cache almost every lookup results in (slow) reading from the RAM. CatBoost models are small enough to fit into the cache. There was a single operation type of model application in our tests, so the CatBoost models stayed persistently in the cache. In real applications, CatBoost model will most likely not stay in the cache alone and will be even slower because of this. On the contrary the performance of the Decision Tensor Ensemble will not degrade due to that fact.
